Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-09 writeup/gz_hubble_data.tex
Figure 10 fixed for #66.
Spell-checked with aspell

Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework. Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution. The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}. Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}. The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors. Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.

@@

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The images used are three-color composites using the $g^\prime$, $r^\prime$, and $i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria. Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source. This resulted in a larger set of 30,339 images. Of the images in the coadded sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.

@@

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.

@@

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each response to a question ($f_{response}$) on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF. Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal. This method is effective, however, at filtering out contributions from random or delibrately malicious classifiers.

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshfts with those at the lowest redshift. \citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.

@@

\subsection{Generating images of artifically-redshifted galaxies}

@@

\begin{figure}
\center
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness. This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
\label{fig:zeta_mu}
\end{figure}

@@

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}. To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either a lack of redshift for the host galaxy or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.

@@

\begin{table}
\center
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:f_vs_f}. Correctable images have a single-valued relationship between their measured \ffeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a non single-valued relationship (blue regions). NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Lower-limit                        & 1,986   & 50\% \\
NEI                                & 80      &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

This section described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task. The following two examples show to use the vote fractions for a particular Task to obtain a sample of galaxies with a certain morpholgical type.

@@

\subsection{Example 2: Identifying clump multiplicity}
Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crutial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}. Simulations show clumps migrate from the outer disk to the galactic center on relatively short (a few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies. GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.

@@

Within the sample of galaxies identified as ``not smooth'', it is clear that the addition of the clumpy branch is necessary to describe a large fraction of the sample; disk-dominated galaxies outnumber clumpy morphologies by less than a factor of 2. Disk galaxies are primarily unbarred \citet{mel14} and possessing two visible spiral arms over a flat distribution of pitch angles and bulge prominences. Clumpy galaxies are identified across the full range of clump multiplicities, with the exception of 1-clump galaxies (which would be difficult to differentiate from compact spheroids). Roughly half of the galaxies have at least 1~clump identified as the brightest; the clumps are most commonly asymmetrically arranged in clusters and are not often seen embedded in larger structures.

@@

The types and accuracies of morphological classification strongly depend on the sample and methods being used. In an attempt to make a consistent comparison between different techniques, galaxies are broadly grouped into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy. These categories are compared to two parameters in GZH: \fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.

@@

Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their automated/expert visual morphologies for each of the six catalogs matched to GZH. The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this may be due to intrisic differences in the galaxies, in the techniques used to measure morphology, or both. The distribution of \fbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends. Early-type galaxies are at their highest proportion at \fbest$\sim0$, but constitute only 40\% of the galaxies at most. In contrast, GOODS galaxies at low \fbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \fbest$\sim0.2$. In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$. Visual inspection of images of galaxies where both \fbest{} and $n$ are high show that the majority are obvious spirals but with prominent bulges, indicating that the single-component \sersic{} fit is likely choosing too small of an effective radius and missing the extended disk structure for a large population of galaxies.

@@

Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a strong correlation between \ffeatures{} for both sets of images. The mean change in \ffeatures{} from the shallow to full depth images  $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$. While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification. Defining a clean sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology. Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology. Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.

@@

To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simluated \ferengi{} images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}). A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data. This requirement was only met for Task~01, which significantly reduced the goodness-of-fit for the model functions as compared with to the smooth/features task. Here we show an example of results obtained for the bar Task. Figure~\ref{fig:f_vs_fbar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $f_\mathrm{bar,z=0.3}$. Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as compared to 2\% for $f_\mathrm{features}$. Similar results were obtained for all higher-order Tasks in GZH, as described in Section~\ref{ssec:higher_order_tasks}.

@@

\begin{table}ー
\label{tbl:ferengi_bar}
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:f_vs_fbar}. Correctable images had a single-valued relationship between their measured \fbar{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_fbar}). Galaxies with a lower-limit on \fbar{} had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions). Only 17\% (maximum) of \ferengi{} galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.   \label{tbl:ferengi_bar_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 664   & 17\% \\
Lower-limit                        & 483   & 12\% \\
NEI                                & 2,803     & 71\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

>>>>

Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework. Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution. The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}. Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}. The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors. Morphologies of individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density contrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.

@@

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The images used are three-color composites using the $g^\prime$, $r^\prime$, and $i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria. Co-added images from Stripe~82 were selected from the union of galaxies with co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a co-add source. This resulted in a larger set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.

@@

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.

@@

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each response to a question ($f_{response}$) on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF. Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal. This method is effective, however, at filtering out contributions from random or deliberately malicious classifiers.

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshifts with those at the lowest redshift. \citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.

@@

\subsection{Generating images of artificially-redshifted galaxies}

@@

\begin{figure}
\center
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness. This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
\label{fig:zeta_mu}
\end{figure}

@@

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidently applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}. To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either a lack of redshift for the host galaxy or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.

@@

\begin{table}
\center
\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}. Correctable images have a single-valued relationship between their measured \ffeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a non single-valued relationship (blue regions). NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Lower-limit                        & 1,986   & 50\% \\
NEI                                & 80      &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

This section described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task. The following two examples show to use the vote fractions for a particular Task to obtain a sample of galaxies with a certain morphological type.

@@

\subsection{Example 2: Identifying clump multiplicity}
Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crucial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}. Simulations show clumps migrate from the outer disk to the galactic center on relatively short (a few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies. GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.

@@

Within the sample of galaxies identified as ``not smooth'', it is clear that the addition of the clumpy branch is necessary to describe a large fraction of the sample; disk-dominated galaxies outnumber clumpy morphologies by less than a factor of 2. Disk galaxies are primarily unbarred \citet{mel14} and possessing two visible spiral arms over a flat distribution of pitch angles and bulge prominence. Clumpy galaxies are identified across the full range of clump multiplicities, with the exception of 1-clump galaxies (which would be difficult to differentiate from compact spheroids). Roughly half of the galaxies have at least 1~clump identified as the brightest; the clumps are most commonly asymmetrically arranged in clusters and are not often seen embedded in larger structures.

@@

The types and accuracy of morphological classification strongly depend on the sample and methods being used. In an attempt to make a consistent comparison between different techniques, galaxies are broadly grouped into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy. These categories are compared to two parameters in GZH: \fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.

@@

Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their automated/expert visual morphologies for each of the six catalogs matched to GZH. The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this may be due to intrinsic differences in the galaxies, in the techniques used to measure morphology, or both. The distribution of \fbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends. Early-type galaxies are at their highest proportion at \fbest$\sim0$, but constitute only 40\% of the galaxies at most. In contrast, GOODS galaxies at low \fbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \fbest$\sim0.2$. In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$. Visual inspection of images of galaxies where both \fbest{} and $n$ are high show that the majority are obvious spirals but with prominent bulges, indicating that the single-component \sersic{} fit is likely choosing too small of an effective radius and missing the extended disk structure for a large population of galaxies.

@@

Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a strong correlation between \ffeatures{} for both sets of images. The mean change in \ffeatures{} from the shallow to full depth images  $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$. While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification. Defining a clean sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology. Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or vice versa, while the rest would transition to or from the ``intermediate'' morphology. Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.

@@

To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simulated \ferengi{} images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}). A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data. This requirement was only met for Task~01, which significantly reduced the goodness-of-fit for the model functions as compared with to the smooth/features task. Here we show an example of results obtained for the bar Task. Figure~\ref{fig:f_vs_fbar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $f_\mathrm{bar,z=0.3}$. Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as compared to 2\% for $f_\mathrm{features}$. Similar results were obtained for all higher-order Tasks in GZH, as described in Section~\ref{ssec:higher_order_tasks}.

@@

\begin{table}ー
\label{tbl:ferengi_bar}
\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_fbar}. Correctable images had a single-valued relationship between their measured \fbar{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_fbar}). Galaxies with a lower-limit on \fbar{} had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions). Only 17\% (maximum) of \ferengi{} galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.   \label{tbl:ferengi_bar_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 664   & 17\% \\
Lower-limit                        & 483   & 12\% \\
NEI                                & 2,803     & 71\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}
